---
title: "Lab 01 - Hello R - Exercise"
author: "Lan Zhang"
date: "2021-September-12"
output: 
  html_document: 
    fig_height: 4
    fig_width: 5
    highlight: pygments
    theme: cerulean
---

### Load packages

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```


### Exercise 1

(Type your answer to Exercise 1 here. This exercise does not require any R code.)
```{r}
dim(datasaurus_dozen)

datasaurus_dozen %>% 
  count(dataset) %>% 
  print() #show all the variables/datasets

```

### Exercise 2

(The answers for this Exercise are given for you below. But you should clean up some of the narrative so that it only includes what you want to turn in.)

First let's plot the data in the dino dataset:

```{r plot-dino, fig.height=3, fig.width=6}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")

ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()

# or
plot(dino_data$x, dino_data$y, pch=20)
```

And next calculate the correlation between `x` and `y` in this dataset:

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
# or
cor(dino_data$x, dino_data$y)
```

### Exercise 3

(Add code and narrative as needed. Note that the R chunks are labeled with `plot-star` and `cor-star` to provide spaces to place the code for plotting and calculating the correlation coefficient. To finish, clean up the narrative by removing these instructions.)

```{r plot-star}
star_data <- datasaurus_dozen %>%
  filter(dataset == "star")
ggplot(data = star_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

I'm some text, you should replace me with more meaningful text...

```{r cor-star}
star_data %>%
  summarize(r = cor(x, y))
# correlation coefficient for star dataset is larger than the one for dino data.
```

### Exercise 4

(Add code and narrative as needed. Note that two R chunks are given but they are not labeled. Use the convention from above to name them appropriately.)

```{r}
circle_data <- datasaurus_dozen %>%
  filter(dataset == "circle")
ggplot(data = circle_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

```{r}
circle_data %>%
  summarize(r = cor(x, y))
# correlation coefficient for star dataset is smaller than the one for dino data.
```

### Exercise 5

(Add code and narrative as needed. To add R chunks either type out the backticks, curly braces, and the letter `r` or use the Insert chunk button above, green C+.)

```{r}
# plotting all datasets inside datasaurus_dozen
ggplot(datasaurus_dozen, aes(x = x, y = y, color = dataset))+
  geom_point()+
  facet_wrap(~ dataset, ncol = 3) +
  theme(legend.position = "none")

# print all correltaion coefficients for each dataset
datasaurus_dozen %>%
  group_by(dataset) %>%
  summarize(r = cor(x, y)) %>%
  print(13)
```
